\LaTeX{} 笔记模板

### 2022-10-29 note-temp/main-en.tex
update

%\documentclass[en,hazy,screen,blue,14pt]{elegantnote}

\documentclass[en,normal,11pt,blue]{elegantnote}
\usepackage{epsfig,amssymb,amsmath,version}
\usepackage{amssymb,version,graphicx,fancybox,mathrsfs,multirow}
%\usepackage[notcite,notref]{showkeys}
\usepackage{diagbox}
\usetikzlibrary{arrows,shapes}

\usepackage{tocloft}
\renewcommand{\cfttoctitlefont}{\hfill \bfseries \LARGE}
\renewcommand{\contentsname}{\centerline{\color{ecolor}Contents}}
\renewcommand{\cftaftertoctitle}{\hfill}
\setlength{\cftbeforetoctitleskip}{10ex}
\setlength{\cftaftertoctitleskip}{5ex}
\renewcommand{\cftsecdotsep}{\cftdotsep} 
\renewcommand{\cftbeforesecskip}{3ex}
\renewcommand{\cftbeforesubsecskip}{1ex}

\title{ElegantNote: An Elegant \LaTeX{} Template for Notes}

\author{Dongsheng Deng}
\institute{Elegant\LaTeX{} Program}

\version{2.30}
\date{\today}

\begin{document}
\maketitle

\pagenumbering{Roman}

%\input{Cover.tex}
%\clearpage

% ----- generate a empty page -----
%\newpage\null\thispagestyle{empty}\newpage \addtocounter{page}{-1}
%\addtocounter{page}{-1}

\vskip -2em
\tableofcontents
\clearpage

@@

@@

This update is to resolve \TeX{} Live 2020 compilation errors caused by \lstinline{gbt7714} compatibility issues.

@@

\section{Recruit Support Members}

Recruit support members for Elegant\LaTeX{} to translate template official guide, maintain wiki entries, update Wechat articles. No deadline for this recruitment.

So far, Elegant\LaTeX{} has four support members:
\begin{itemize}
	\item OG Translator: \href{https://github.com/peggy2006xzyz}{YPY};
	\item Wiki Maintainer: \href{https://github.com/izinngo}{Ingo Zinngo}, \href{https://github.com/xiaohao890809}{Xiaohao890809};
	\item QQ Group Manager: \href{https://github.com/sikouhjw}{Sikouhjw}.
\end{itemize}

Thank them all!!!

\section{Acknowledgement}
The number of stars on GitHub for ElegantPaper reached 176 on April 12, 2020 at the release of ElegantNote v2.20.
Thank China\TeX{} and \href{http://www.latexstudio.net/}{\LaTeX{} studio} for their promotion.

If you like our templates, star on GitHub.
\begin{figure}[!ht]
	\centering
	\includegraphics[width=\textwidth]{star.png}
	\caption{Twinkle, Twinkle, Little Star}
\end{figure}

\section{Donation}
To express your love for our templates and/or our developers, please do not hesitate to tip us.
\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.4\textwidth]{donate.jpg}
\end{figure}

\textbf{The explanation right of the tip usage belongs to Elegant\LaTeX{} with no supervision. Feel free to tip us.} Those who donate more than 10 RMB will be recorded in the donation list and will receive a donation certificate. Thank all the tippers!

\begin{table}[htbp]
  \centering
  \scriptsize
  \caption{Donation List}
    \begin{tabular}{cccccccc}
    \toprule
    \textbf{Tipper} & \textbf{Amount} & \textbf{Date} & \textbf{Channel} & \textbf{Tipper} & \textbf{Amount} & \textbf{Date} & \textbf{Channel} \\
    \midrule
    Lerh  & 10 RMB & 2019/05/15 & Wechat    & yueguodipingxian & 10 RMB & 2019/05/15 & Wechat \\
	  yinsang    & 20 RMB & 2019/05/27 & Wechat    & *kong    & 10 RMB & 2019/05/30 & Wechat \\
	  latexstudio.net & 666 RMB & 2019/06/05 & Alipay   & A*n   & 40 RMB & 2019/06/15 & Wechat \\
	  * xia   & 22 RMB & 2019/06/15 & Wechat    & * qian  & 21 RMB  & 2019/06/15 & Wechat \\
	  Cassis & 11 RMB & 2019/06/30 & Wechat    & * jun    & 10 RMB & 2019/07/23 & Wechat \\
	  P*u   & 50 RMB & 2019/07/30 & Wechat    & * meng    & 19 RMB & 2019/08/28 & Wechat \\
	  Qu Doudou   & 10 RMB & 2019/08/28 & Wechat    & Li Bo    & 100 RMB & 2019/10/06 & Wechat \\
	  Njustsll & 10 RMB & 2019/10/11 & Wechat    & Liu Zhikuo   & 99.99 RMB & 2019/10/15 & Alipay \\
	  * tao   & 16 RMB & 2019/10/17 & Wechat    & Chini    & 12 RMB & 2019/10/17 & Alipay \\
	  yuanfengjing & 10 RMB & 2019/10/28 & Wechat    & Guo Deliang   & 88 RMB & 2019/11/03 & Wechat \\
	  ziqiangbuxi  & 20 RMB & 2019/11/04 & Alipay   & dushuzhichong  & 20 RMB & 2019/11/18 & Wechat \\
	  * deng    & 10 RMB & 2019/11/18 & Wechat    & * zhe   & 20 RMB & 2019/11/18 & Wechat \\
	  anonymous    & 10 RMB & 2019/11/24 & Wechat    & Jiye Qian & 66 RMB & 2019/12/04 & Wechat \\
	  * yang   & 20 RMB & 2019/12/05 & Wechat    & Catcher & 11 RMB & 2019/12/08 & Alipay \\
	  xierbotementu & 10 RMB & 2019/12/09 & Alipay   & * wei   & 10 RMB & 2019/12/09 & Wechat \\
	  Simon & 20 RMB & 2019/12/11 & Alipay   & liushangqianyi & 66.60 RMB & 2019/12/18 & Alipay \\
	  yu     & 10 RMB & 2019/12/20 & Alipay   & *chen   & 15 RMB & 2019/12/20 & Wechat \\
	  suifeng   & 20 RMB & 2019/12/27 & Alipay   & Ws    & 23.30 RMB & 2019/12/28 & Wechat \\
	  chuba    & 100 RMB  & 2020/01/02 & Alipay   & p*e   & 20 RMB & 2020/01/03 & Wechat \\
	  Shunmx & 100 RMB & 2020/01/03 & Wechat    & hj    & 10 RMB & 2020/01/03 & Wechat \\
	  F*5   & 10 RMB & 2020/01/03 & Wechat    & S*m   & 20.20 RMB & 2020/01/03 & Wechat \\
	  erdaiqingzhi  & 13 RMB & 2020/01/14 & Alipay   & *?    & 66 RMB & 2020/01/15 & Wechat \\
	  Mr. Xiong & 20 RMB & 2020/01/17 & Wechat    & *bo    & 15 RMB & 2020/01/18 & Wechat \\
	  *Zhe    & 10 RMB & 2020/02/02 & Wechat    &  Jackie &  88.80 RMB  &  2020/02/09 & Wechat \\
	  Henry\_Sun & 50 RMB & 2020/02/14 & Alipay & * Qiao  & 50 RMB & 2020/02/21 & Wechat \\
	  YunLian & 10 RMB & 2020/03/02 & Alipay & S*y  &  10 RMB  &  2020/03/15 & Wechat \\
	  * Ge  & 66.66 RMB & 2020/03/17 & Wechat    &   K*e & 30 RMB & 2020/03/30 & Wechat\\
	  * Yang  &  20 RMB  &  2020/04/02 & Wechat & Shi*n  & 30 RMB & 2020/04/11 & Wechat \\
\bottomrule
\end{tabular}%
  \label{tab:donation}%
\end{table}%

@@

>>>>

%!TEX program = xelatex
%\documentclass[en,hazy,normal,blue,11pt]{elegantnote}
\documentclass[en,normal,12pt,blue]{elegantnote}
\usepackage{amssymb,mathrsfs,multirow}
%\usepackage[notcite,notref]{showkeys}
%\usepackage{epsfig}
%\usepackage{tabularx}
\usepackage{diagbox}
%\usepackage{bookmark}
\usetikzlibrary{arrows,shapes}
\usepackage{array,makecell}
%\usepackage{tikz}
%\usepackage{tikzpagenodes}
%\usetikzlibrary{shapes.geometric,shapes.symbols,shapes.callouts,decorations.markings,shapes.misc,shapes.arrows}

\usepackage[numbers,sort&compress]{natbib}
\def\bibfont{\small}      % 修改参考文献字体
\setlength{\bibsep}{8pt}  % 调整参考文献间距
%\usepackage{subfig}

% --- 算法宏包及设置 ---
\usepackage{algorithm}
\usepackage{algpseudocode}
\floatname{algorithm}{Algorithm}
\algrenewcommand\algorithmicrequire{\textbf{Input:}}
\algrenewcommand\algorithmicensure{\textbf{Output:}}

% --- 代码高亮 ---
%\input{matlab-style.tex}

%\definecolor{hong}{RGB}{199,21,133}
%\definecolor{huang}{RGB}{255,164,0}

%\makeatletter
%\newcommand\HUGE{\@setfontsize\Huge{32}{36}}
%\makeatother

%\bibliographystyle{thuthesis-numeric}
\bibliographystyle{plain}

% --- 自定义命令 -----
\newcommand{\CC}{\ensuremath{\mathbb{C}}}
\newcommand{\RR}{\ensuremath{\mathbb{R}}}
\newcommand{\A}{\mathcal{A}}
\newcommand{\ii}{\bm{\mathrm{i}}\,}  % 虚部
\newcommand{\bA}{\boldsymbol{A}}
\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\blue}[1]{\textcolor{blue}{#1}}
\newcommand{\mT}{\mathrm{T}}
\newcommand{\md}{\mathrm{d}}

%\title{\LaTeX 笔记模板}
%\author{某某某}
%\institute{}
%\version{1.3}
%\date{\zhtoday}
%\date{}

\begin{document}
%\maketitle

\pagenumbering{Roman} % 页码为大写罗马数字

\input{cover2.tex}

% ----- generate a empty page -----
%\clearpage%
%\thispagestyle{empty}%
%\addtocounter{page}{-1}%
%\null%
%\clearpage

\clearpage
%\phantomsection
\pdfbookmark[1]{Contents}{toc}
\tableofcontents
\clearpage
\setlist[itemize]{label=$\circ$}

@@

%==========================================%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 正文内容从这里开始  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

Citation \cite{Tadmor2012} and \cite{Adams2003,TreWei2014}.  Citation \cite{Adams2003,Shen1994}.

\section{Acknowledgement}

Thank \href{https://github.com/sikouhjw}{sikouhjw} and \href{https://github.com/syvshc}{syvshc} for their quick response to Github issues and continuously support work for ElegantLaTeX. Thank ChinaTeX and \href{http://www.latexstudio.net/}{LaTeX Studio} for their promotion.

@@

%%%%%%%%%%%%%%%%%%%%%%%% 参考文献 %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\phantomsection
\addcontentsline{toc}{section}{References} % 添加  "参考文献 " 到目录

% 生成参考文献, 使用第一种请把第二种全部注释

% 第一种方式, 使用 bib 文件

%\nocite{*}  % 可以暂时显示全部参考文献, 包括未引用的

\bibliography{reference}

% 第二种方式, 按照格式直接写文献信息, 使用第二种请把第一种全部注释

%\begin{thebibliography}{99}
%\bibitem{Tadmor2012} Tadmor~E. A review of numerical methods for nonlinear partial differential
%  equations\allowbreak[J]. Bull. Amer. Math. Soc., 2012, 49(4): 507-554.
%
%\bibitem{LiLiu1997} 李荣华, 刘播. 微分方程数值解法\allowbreak[M]. 东南大学出版社, 1997.
%
%\bibitem{Adams2003} Adams~R~A, Fournier~J~J~F. Sobolev spaces\allowbreak[M]. Elsevier, 2003.
%
%\bibitem{TreWei2014}Trefethen~L~N, Weideman~J~A~C. The exponentially convergent trapezoidal rule\allowbreak[J]. SIAM Rev., 2014, 56(3): 385-458.
%
%\bibitem{Shen1994} Shen~J. Efficient spectral-Galerkin method I. Direct solvers of second- and fourth-order equations using Legendre polynomials\allowbreak[J]. SIAM J. Sci. Comput., 1994, 15(6): 1489-1505.
%
%\end{thebibliography}

%\printbibliography[heading=bibintoc, title=\ebibname]
